XXX

### 2012-03-25 paper/engNERwiki.tex
references rendberakva nagyjabol, plusz dolgok a magyar reszhez

In this paper we present a kind of combination of the approaches mentioned above. We built NE-tagged corpora for English and Hungarian -- fully automatically generated from Wikipedia. %Our goal was to create gold standard corpora which can serve as train, devel and test datasets for automatic NE-taggers.

@@

\section{Wikipedia and NER}
\label{sec:related}
% Wikify!
% stuff from Mining Meaning from Wikipedia
%NER and Wikipedia

Wikipedia is a free, multilingual Internet encyclopedia, written collaboratively by volunteers. (CITE http://en.wikipedia.org/wiki/Wikipedia). It is a goldmine of information; at the time of writing, Wikipedia contains about 21 million interlinked articles. Of these, 3,903,467 are English and 212,120 are Hungarian. XXX

Wikipedia has been applied for several NLP tasks, e.g.~word sense disambiguation, ontology and thesaurus building, multilingual Information Retrieval, and Question Answering, as Medelyan et al.~\shortcite{Medelyan:09} point out in their fully detailed survey about mining meaning from Wikipedia.

Wikipedia is recognized as one of the largest available collection of entities, and also as an external knowledge to improve the accuracy of NER. The most obvious utilization of Wikipedia for NER is extracting gazetteers containing person names, locations or organizations (e.g. Toral and Munoz \shortcite{Toral:06}). Creating dictionaries of entities is also a common step of named entity disambiguation \cite{Bunescu:06,Cucerzan:07}. Not only supervised systems use lists generated from Wikipedia: Nadeau et al. \shortcite{Nadeau:06} use similar lists in an unsupervised NER system.

Wikipedia's knowledge may be incorporated as features in NER learning, e.g. Kazama and Torisawa \shortcite{Kazama:07} showed that automatic extraction of category labels from Wikipedia improves the accuracy of a supervised NE-tagger.

@@

In contrast to the aforementioned methods, we applied a new approach to recognize and classify NEs in the corpora generated from Wikipedia. We mapped the DBpedia ontology classes to standard NE tags and assigned them to Wikipedia entities (see more details in section \ref{dbpedia}).

To our knowledge, such type of automatically built corpora are not freely available, with the one exception of the Semantically Annotated Snapshot of the English Wikipedia \cite{Zaragoza:07}. It provides a wide range of linguistic information: POS tags, dependency labels, WordNet super senses and NE annotation according to WSJ and CoNLL tagsets. However, they followed a different way: the NEs were tagged by open source softwares. Our corpora is available under the same license as Wikipedia's one (Creative Commons Attribution-Sharealike 3.0 Unported License).

Thanks for the huge amount of Wikipedia articles, the possibility of building large enough (XXX ez mit jelent?) corpora is given for less resourced languages, as well. Since our method is mainly XXX language-independent, it can be easily applied for languages which are structurally differing from English. Hungarian is a highly agglutinative language, with free word order and other particularities XXX detailed later in section \ref{sec:hun}. There are human annotated CoNLL-style datasets, but the one presented here is the first large enough automatically NE-annotated corpus for Hungarian.

\section{Creating the English Corpus}  % Dzsííízösz
\label{sec:create}

Our goal is to create a large NE-annotated corpus, automatically generated from Wikipedia articles. We follow a similar path XXX to \cite{Nothman:08}, who broke up XXX the process into four steps:
\begin{enumerate}
\item Classify all articles into entity classes
\item Split Wikipedia articles into sentences
\item Label \texttt{NE}s according to link targets
\item Select sentences for inclusion in a corpus
\end{enumerate}

In this section, we describe how these steps were implemented. While the approach in essence is language-agnostic, the exact details XXX have to be accomodated to the target language. This section explains the general idea and its execution for English; the next section describes how the idea can be adapted to Hungarian.

@@

Wikipedia is very rich source of information; aside from the article text, a huge amount of data is encompassed in infoboxes, templates and the category structure. Our task requires the use of only the links between the articles and the article text. In addition to in-article links, our method takes advantage of the redirect and interlanguage links, available as SQL dumps.

@@

The English corpus is based on the Wikipedia snapshot as of January 15, 2011. The XML files were parsed with the \texttt{mwlib} (CITE http://code.pediapress.com) parser. The raw text was tokenized with a modified version of the Punkt sentence and word tokenizers \cite{Kiss:06} in NLTK \cite{Loper:02}. The words were lemmatized with the Wordnet lemmatizer, also in NLTK, and POS tagged with HunPos \cite{Halacsy:07}.

@@

Many authors, such as Kazama and Torisawa \shortcite{Kazama:07} and Nothman et al \shortcite{Nothman:09} used unsupervised methods based on Wikipedia categories and text to classify articles into entity categories. To avoid the inevitable classification errors, we obtain entity type information from the DBpedia knowledge base \cite{Bizer:09}. This enables us to have high precision information about entity types at the expense of recall: out of the 3,903,467 English Wikipedia pages, 1,470,293 are covered by DBpedia.

@@

The types in DBpedia are organized into a class hierarchy, available as an OWL (CITE) ontology. The ontology contains the 320 most frequent entity categories, arranged into a taxonomy under the base class \texttt{owl:Thing}. Most of the classes belong into the 5 largest sub-hierarchies (here named after their topmost classes XXX): \texttt{Agent} (which is further divided into \texttt{Person} and \texttt{Organisation}), \texttt{Event}, \texttt{Place}, \texttt{Species} and \texttt{Work}. The taxonomy is rather flat: the top level contains 44 classes and there are several nodes with a branching factor of 20.

The type of entities is extracted automatically from Wikipedia categories. However, the mapping between Wikipedia categories and classes in the DBpedia ontology is manually defined. This, together with the fact that the existance of the reference ontology prevents the proliferation of categories observable in Wikipedia \cite{Bizer:09}, ensures that type information in DBpedia can be considered gold quality.

It is not difficult to see the parallels XXX between the DBpedia sub-hierarchies \texttt{Person}, \texttt{Organisation} and \texttt{Place} and the ConLL NER categories \texttt{PER}, \texttt{ORG} and \texttt{LOC}. The fourth category, MISC is more elusive; according to the ConLL NER annotation guide (CITE?: http://www.cnts.ua.ac.be/conll2003/ner/annotation.txt), the sub-hierarchies \texttt{Event} and \texttt{Work} belong to this category, as well as various other class outside the main sub-hierarchies.

While the correspondence described above holds for most classes in the XXX sub-hierarchies, there are some exceptions. For instance, the class \texttt{SportsLeague} is part of the \texttt{Organisation} sub-hierarchy, but in the ConLL corpus, sport leagues are tagged as MISC. Similarly, the class \texttt{SportsTeamSeason} is under \texttt{Event}, by which account it would be classified as MISC; however, ConLL does not recognize such entities. To account for these misclassification, as well as the miscellaneous classes outside the main hierarchies, we have introduced a mapping mechanism. We created a file of DBpedia class -- NER category mappings. Whenever an entity is evaluated, we look up its class, as well as the ancestors of its class, in the mapping, and assign to the entity the category of the class that matches it most closely -- i.e. the category of the entity's class, if it is in the list, or that of its closest ancestor. XXX!!! If no match is found, the entity is tagged with \texttt{O}. Since we take advantage of the inheritance hierarchy, the mapping list remains short: it contains only the root classes of the main sub-hierarchies, exceptions of the like XXX mentioned above and the various classes that belong to the MISC category according to the ConLL annotation guideline.

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph (CITE). This introduces the problem of selecting the right superclass, and hence, ConLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}. There are two ways to tackle this problem. The first is to follow the DBpedia guidelines and only retain the first parent. The second method is manually deciding the right NER mapping for the ambiguous XXX class and adding it to the mapping file. The first approach, unfortunately, already fails to assign the correct ConLL NER tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation; ConLL's LOC. Therefore, only the second, manual approach ensures correct tagging. XXX

@@

%We elected to use the CoNLL NE types. stb.

@@

Our approach to entity identification relies on Wikipedia cross-references found in the article text. We assume that individual Wikipedia articles describe named entities. A link to an article can then be perceived as a mapping that identifies its anchor text with a particular entity. However, there are exceptions to this rule. Disambiguation pages are used when the page title is ambiguous, and can refer to several entities. If a link points to a disambiguation page, we acknowledge the anchor text as an entity, but mark it unknown. A similar measure is taken if the link target XXX does not exist. Links to redirect pages are resolved to point instead to the redirect target, after which they are handled as regular cross-references.

@@

%Both approaches are evaluated in the next chapter.

%Szerintem ide kéne a DBpedia--CoNLL mapping
We use DBpedia as

@@

Strictly speaking, our original assumption of equating Wikipedia articles with named entities is not valid: many pages describe common nouns (Book, Aircraft), numbers (1, 42), currencies (Euro, Dollar) or other concepts that fall outside the scope of NER. In this section, we describe the measures taken to avoid errors introduced by these false entities. We shall modify the two approaches -- precision and recall-oriented -- accordingly.

Proper entities that are not deemed NE under the ConLL scheme cause XXX little concern: they are either missing from DBpedia altogether, or we can map the classes they belong to to the NER category \texttt{0} (not an entity). This "ontological filtering" ensures that we need no adjustment XXX to our original method.

Links to number and common noun pages are handled differently by the two approaches. The precision-oriented method treats them similarly to links to unknown entities and discards the sentences in which they occur. The recall-oriented approach tries to distinguish them from links to entities so that otherwise valid training sentences can be retained XXX. The method is as follows XXX.
\begin{itemize}
\item Common nouns are filtered by POS category: links that contain no proper nouns are ignored.
\item Numbers behave more like proper nouns in that they can refer to entities, such as 737 to the Boeing 737. Therefore, links to number pages are filtered by the surface form of the page title.
\end{itemize}

@@

from \cite{Nothman:09}: Exceptions are made for common titlecase words, e.g. I, Mr., June, and sentence-initial words.

@@

There are many incomplete sentences in the Wikipedia text: image captions, enumerations items, contents of table cells, etc. On the one hand, these sentence fragments may prove to be of too low quality to be of any use in the traditional NER task. On the other hand, they could prove to be invaluable when training a named entity recognizer for user generated content. We have added a post-filtering step to recognize and label these fragments, so that users of the corpus can decide what to do with them. XXX

Manual inspection has found two conditions that can be used to detect fragments. A sentence is labelled as such if it either lacks a punctuation mark at the end or it contains no finite verbs. Our final corpus contains STAT full sentences and STAT fragments.
% TODO: Last sentence to evaluation? But then this whole subsection is too short.

@@

In Wikipedia the nationalities (e.g. American and Australian) links to the corresponding places (America and Australia, respectively). However, in CoNLL scheme these types of entities take parts of MISC category. XXX Postprocessing: list look-up (nationalities, adjective forms of person who live in the corresponding country); if the name is POS-tagged as adjective, then it is not a NE

%nem biztos, hogy ide kell
Link boundaries need to be adjusted, e.g. to remove excess punctuation.

@@

The procedure described in the previous section was used to generate the Hungarian corpus as well. However, Hungarian differs from English in several aspects: as a language, in data and tool coverage and NER practices. In this section we describe these differences and the changes they prompted in the algorithm.

@@

While NLTK has excellent tools for English, Hungarian is not supported. Therefore, we worked with the tools developed by the Hungarian computational linguist community. For sentence tokenization we used an in-house statistical chunker tailored for Hungarian. It has been trained on the Szeged corpus and it handles the peculiarities of Hungarian ortography, such as the periods placed after numbers in date expressions. Although HunPos, as its name implies, is fully capable of POS tagging Hungarian text, we opted for Hunmorph (CITE), a morphological analyzer that, apart from PAS tagging, also lemmatizes the words. Hundisambig (CITE) was used to select the right analysis based on the word context\footnote{Incidentally, Hundisambig relies on HunPos for its HMM model.}.

The Hungarian part-of-speech taggers output KR codes (CITE). In addition to the POS category, the KR code also includes inflection information, such as the number, person and case XXX, which makes it much better suited to agglutinative languages than Penn Treebank POS tags. One shortcoming of the KR code is that it does not differenciate between common and proper nouns. Since in Hungarian only proper nouns are capitalized, we can usually decide whether a noun is proper or not based on the initial letter. However, this rule cannot be used if the noun is at the beginning of a sentence, as words at the beginning of sentences are always capitalized. Hence, all sentences that begin with nouns have been removed from the corpus.

@@

% vs. ConLL / Szeged
% Corpus sizes, performance, tagging conventions
% Hun -> not utf-8, loss of precision?
%measuring Wikipedia's inconsistency using n-gram tag variation (\cite{Nothman:09})
%ez jó mérőszám lehet a gold standard korpuszok összehasonlítására
%használhatjuk fordítva is: ha egy adott nucleus ugyanolyan n-gram környezetben nagyon sokszor van X-ként taggelve, és kevésszer Y-ként, akkor az Y-okat is átcsinálhatnánk X-szé

@@

To evaluate our corpora we used a maximum entropy NE-tagger \cite{Varga:07}, which was originally developed for labeling NEs in Hungarian texts, but it can be tuned for different languages, as well. The feature set was as follows:

@@

However, Wikipedia-derived corpora can also be used for improving NER performance in other ways. First, we collected huge gazetteer lists from the corpus for each NE category, which improved the overall F-measure given to the NE-tagger training and testing on CoNLL dataset. A second trial was labeling the CoNLL datasets by the model trained on Wikipedia corpus, and giving these labels as extra features to the next CoNLL train. Both methods result in improved overall F-measure on CoNLL test set.

@@

az eredeti DBPedia osztályokat is megtarthatnánk, hiszen nem mindig célravezető a CoNLL osztályok használata, mivel azok elég tág kategóriák, amikbe olyan dolgok is tartoznak, amik nagyon eltérőek is lehetnek

@@

@@

@@

\bibitem[\protect\citename{Nothman \bgroup et al.\egroup}2009]{Nothman:09}
\newblock 2009.
\newblock Analysing Wikipedia and Gold-Standard Corpora for NER Training.
\newblock In: {\em Proceedings of the 12th Conference of the European Chapter of the ACL}, pages 612--620.

\bibitem[\protect\citename{Toral and Munoz}2006]{Toral:06}
A. Toral and R. Munoz.
\newblock 2006.
\newblock A proposal to automatically build and maintain gazetteers for Named Entity Recognition by using Wikipedia.
\newblock In: {\em EACL 2006}.

\bibitem[\protect\citename{Loper \bgroup et al.\egroup}2002]{Loper:02}
Edward Loper, Steven Bird.
\newblock 2002.
\newblock NLTK: the Natural Language Toolkit. 
\newblock In: {\em Proceedings of the ACL-02 Workshop on Effective tools and methodologies for teaching natural language processing and computational linguistics}, Volume 1, pages 63--70.

\bibitem[\protect\citename{Loper \bgroup et al.\egroup}2002]{Kiss:06}
Tibor Kiss, Jan Strunk.
\newblock 2006.
\newblock Unsupervised Multilingual Sentence Boundary Detection. 
\newblock In: {\em Computational Linguistics}, 32 (4): pages 485--525.

>>>>

In this paper we present a kind of combination of the approaches mentioned above. We built freely available NE-tagged corpora for English and Hungarian -- fully automatically generated from Wikipedia. %Our goal was to create gold standard corpora which can serve as train, devel and test datasets for automatic NE-taggers.

@@

\section{Wikipedia and NER}
\label{sec:related}
% Wikify!

Wikipedia is a free, multilingual Internet encyclopedia, written collaboratively by volunteers\footnote{http://en.wikipedia.org/wiki/Wikipedia}. It is a goldmine of information; at the time of writing, Wikipedia contains about 21 million interlinked articles. Of these, 3,903,467 are English and 212,120 are Hungarian. XXX %kell ez ide?

Wikipedia has been applied for several NLP tasks, e.g.~word sense disambiguation, ontology and thesaurus building, multilingual information retrieval, and question answering, as Medelyan et al.~\shortcite{Medelyan:09} point out in their fully detailed survey about mining meaning from Wikipedia.

Wikipedia is recognized as one of the largest available collection of entities, and also as an external knowledge to improve the accuracy of NER. The most obvious utilization of Wikipedia for NER is extracting gazetteers containing person names, locations or organizations (e.g.~Toral and Mu\~noz \shortcite{Toral:06}). Creating dictionaries of entities is also a common step of named entity disambiguation \cite{Bunescu:06,Cucerzan:07}. Not only supervised systems use lists generated from Wikipedia: Nadeau et al.~\shortcite{Nadeau:06} use similar lists in an unsupervised NER system.

Wikipedia's knowledge may be incorporated as features in NER learning, e.g.~Kazama and Torisawa \shortcite{Kazama:07} showed that automatic extraction of category labels from Wikipedia improves the accuracy of a supervised NE-tagger.

@@

In contrast to the aforementioned methods, we applied a new approach to recognize and classify NEs in corpora generated from Wikipedia. We mapped the DBpedia ontology classes to standard NE tags and assigned them to Wikipedia entities (see more details in section \ref{dbpedia}).

To our knowledge, such type of automatically built corpora are not freely available, with the one exception of the Semantically Annotated Snapshot of the English Wikipedia \cite{Zaragoza:07}. It provides a wide range of linguistic information: POS tags, dependency labels, WordNet super senses and NE annotation according to WSJ and CoNLL tagsets. However, they followed a different way: the NEs were tagged by high quality open source softwares. Our corpora is available under the same license as Wikipedia's one (Creative Commons Attribution-Sharealike 3.0 Unported License).

Thanks for the huge amount of Wikipedia articles, the possibility of building large enough 
%(XXX ez mit jelent?) elég nagy :)
corpora is given for less resourced languages, as well. Since our method is mainly XXX language-independent, it can be easily applied for languages which are structurally differing from English. Hungarian is a highly agglutinative language, with free word order and other particularities XXX detailed later in section \ref{sec:hun}. There are human annotated CoNLL-style datasets, but the one presented here is the first automatically NE-annotated corpus for Hungarian.

\section{Creating the English Corpus} 
\label{sec:create}

Our goal is to create a large NE-annotated corpus, automatically generated from Wikipedia articles. We follow a similar path XXX to \cite{Nothman:08}, who broke up XXX the process into four steps:

\begin{enumerate}
\item Classify all articles into entity classes.
\item Split Wikipedia articles into sentences.
\item Label NEs according to link targets.
\item Select sentences for inclusion in the corpus.
\end{enumerate}

In this section, we describe how these steps were implemented. While the approach in essence is language-independent, the exact details XXX have to be accomodated to the target language. This section explains the general idea and its execution for English; the next section describes how the idea is adapted to Hungarian.

@@

Wikipedia is a very rich source of information; aside from the article text, a huge amount of data is encompassed in infoboxes, templates and the category structure. Our task requires the use of only the links between the articles and the article text. In addition to in-article links, our method takes advantage of the redirect and interlanguage links, available as SQL dumps.

@@

The English corpus is based on the Wikipedia snapshot as of January 15, 2011. The XML files were parsed with the \texttt{mwlib} parser\footnote{http://code.pediapress.com}. The raw text was tokenized with a modified version of the Punkt sentence and word tokenizers \cite{Kiss:06} in NLTK \cite{Loper:02}. The words were lemmatized with the Wordnet Lemmatizer, also in NLTK, and POS tagged with HunPos \cite{Halacsy:07}.

@@

Many authors, such as Kazama and Torisawa \shortcite{Kazama:07} and Nothman et al.~\shortcite{Nothman:08} used semi-supervised methods based on Wikipedia categories and text to classify articles into entity categories. To avoid the inevitable classification errors, we obtain entity type information from the DBpedia knowledge base \cite{Bizer:09}. This enables us to have high precision information about entity types at the expense of recall: out of the 3,903,467 English Wikipedia pages, 1,470,293 are covered by DBpedia.

@@

The types in DBpedia are organized into a class hierarchy, available as an OWL\footnote{http://www.w3.org/TR/owl-ref/} ontology. The ontology contains the 320 most frequent entity categories, arranged into a taxonomy under the base class \texttt{owl:Thing}. Most of the classes belong into the 5 largest sub-hierarchies (here named after their topmost classes XXX): \texttt{Agent} (which is further divided into \texttt{Person} and \texttt{Organisation}), \texttt{Event}, \texttt{Place}, \texttt{Species} and \texttt{Work}. The taxonomy is rather flat: the top level contains 44 classes and there are several nodes with a branching factor of 20.

The type of entities is extracted automatically from Wikipedia categories. However, the mapping between Wikipedia categories and classes in the DBpedia ontology is manually defined. This, together with the fact that the existence of the reference ontology prevents the proliferation of categories observable in Wikipedia \cite{Bizer:09}, ensures that type information in DBpedia can be considered gold quality.

From the available NER annotation standards we elected to use the CoNLL \cite{Tjong:03} NE types. It is not difficult to see the parallels XXX between the DBpedia sub-hierarchies \texttt{Person}, \texttt{Organisation} and \texttt{Place} and the CoNLL NE categories PERSON, ORGANIZATION and LOCATION. The fourth category, MISCELLANEOUS is more elusive; according to the ConLL NER annotation guide\footnote{http://www.cnts.ua.ac.be/conll2003/ner/annotation.txt}, the sub-hierarchies \texttt{Event} and \texttt{Work} belong to this category, as well as various other classes outside the main hierarchies.

While the correspondence described above holds for most classes in the XXX sub-hierarchies, there are some exceptions. For instance, the class \texttt{SportsLeague} is part of the \texttt{Organisation} sub-hierarchy, but according to the CoNLL annotation scheme, they are tagged as MISC. Similarly, the class \texttt{SportsTeamSeason} is under \texttt{Event}, by which account it would be classified as MISC; however, ConLL does not recognize such entities. To account for these misclassification, as well as the miscellaneous classes outside the main hierarchies, we have introduced a mapping mechanism. We created a file of DBpedia class--NE category mappings. Whenever an entity is evaluated, we look up its class, as well as the ancestors of its class, in the mapping, and assign to the entity the category of the class that matches it most closely -- i.e.~the category of the entity's class, if it is in the list, or that of its closest ancestor. XXX!!! If no match is found, the entity is tagged with \texttt{O}. Since we take advantage of the inheritance hierarchy, the mapping list remains short: it contains only the root classes of the main sub-hierarchies, exceptions of the like XXX mentioned above and the various classes that belong to the MISC category according to the CoNLL annotation guideline.

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph (CITE). This introduces the problem of selecting the right superclass, and hence, CoNLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}. There are two ways to tackle this problem. The first is to follow the DBpedia guidelines and only retain the first parent. The second method is manually deciding the right NE mapping for the ambiguous XXX class and adding it to the mapping file. The first approach, unfortunately, already fails to assign the correct CoNLL NE tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation; while ConLL's one refers it as a Location. Therefore, only the second, manual approach ensures correct tagging. XXX

@@

@@

Our approach to entity identification relies on Wikipedia cross-references found in the article text. We assume that individual Wikipedia articles describe NEs. A link to an article can then be perceived as a mapping that identifies its anchor text with a particular entity. However, there are exceptions to this rule. Disambiguation pages are used when the page title is ambiguous, and can refer to several entities. If a link points to a disambiguation page, we acknowledge the anchor text as an entity, but mark it unknown. A similar measure is taken if the link target XXX does not exist. Links to redirect pages are resolved to point instead to the redirect target, after which they are handled as regular cross-references.

@@

@@

Strictly speaking, our original assumption of equating Wikipedia articles with NEs is not valid: many pages describe common nouns (Book, Aircraft), numbers (1, 42), currencies (Euro, Dollar) or other concepts that fall outside the scope of CoNLL tagset or of NER in general. In this section, we describe the measures taken to avoid errors introduced by these false entities. We shall modify the two approaches -- precision and recall-oriented -- accordingly.

Proper names that are not deemed NE under the ConLL scheme
%ilyeneknek nem szabad lenniük a MISC miatt
 cause XXX little concern: they are either missing from DBpedia altogether, or we can map the classes they belong to to the NER category \texttt{0} (not an entity). This "ontological filtering" ensures that we need no adjustment XXX to our original method.

Links to number and common noun pages are handled differently by the two approaches. The precision-oriented method treats them similarly to links to unknown entities and discards the sentences in which they occur. The recall-oriented approach tries to distinguish them from links to entities so that otherwise valid sentences can be retained XXX. The method is as follows XXX.
\begin{itemize}
\item Common nouns are filtered by POS category: links that contain no proper nouns are ignored.
\item Numbers behave more like proper nouns in that they can refer to entities, such as 737 to the Boeing 737. Therefore, links to number pages are filtered by the surface form of the page title.
\end{itemize}

@@

XXX from \cite{Nothman:09}: Exceptions are made for common titlecase words, e.g. I, Mr., June, and sentence-initial words.

@@

There are many incomplete sentences in the Wikipedia text: image captions, enumerations items, contents of table cells, etc. On the one hand, these sentence fragments may prove to be of too low quality to be of any use in the traditional NER task. On the other hand, they could prove to be invaluable when training a NER tagger for User Generated Content, which is well known to be noisy and fragmented. We have added a post-filtering step to recognize and label these fragments, so that users of the corpus can decide what to do with them. XXX

Manual inspection has found two conditions that can be used to detect fragments. A sentence is labelled as such if it either lacks a punctuation mark at the end, or it contains no finite verbs. Our final corpus contains XXXSTAT full sentences and STAT fragments.
%Ezeket leméred, vagy mérjem én? Ha utóbbi, akkor melyikben kell mérni?
% TODO: Last sentence to evaluation? But then this whole subsection is too short.

@@

In Wikipedia the nationalities (e.g.~American and Australian) links to the corresponding places (America and Australia, respectively). However, in CoNLL scheme these types of entities take parts of MISC category. XXX Postprocessing: list look-up (nationalities, adjective forms of person who live in the corresponding country); if the name is POS-tagged as adjective, then it is not a NE

%nem biztos, hogy ide kell
Link boundaries need to be adjusted, e.g.~to remove excess punctuation.

@@

The procedure described in the previous section was used to generate the Hungarian corpus, as well. However, linguistic diversity pose several problems even in the NER task. In this section we describe the differences between the two languages related to labeling NEs, and the changes they prompted in the algorithm.

@@

Although Hungarian is reckoned to be a less resourced language, and it is not supperted in NLTK, several high quality language processing tools have been developed for Hungarian in recent years. For tokenization and sentence segmentation we used an in-house statistical tool tailored for Hungarian. It has been trained on the largest manually annotated Hungarian corpus \cite{Csendes:04}, and it handles the peculiarities of Hungarian ortography, such as the periods placed after numbers in date expressions. Lemmatization was performed by \texttt{hunmorph} \cite{Tron:05} and \texttt{hundisambig}, latter being an in-house disambiguator to select the right analysis based on the word context.

%Although HunPos, as its name implies, is fully capable of POS tagging Hungarian text, we opted for Hunmorph (CITE), a morphological analyzer that, apart from PAS tagging, also lemmatizes the words. Hundisambig (CITE) was used to select the right analysis based on the word context\footnote{Incidentally, Hundisambig relies on HunPos for its HMM model.}.

The Hungarian morphological analyzer outputs KR-codes \cite{Kornai:04}. In addition to the POS category, the KR-code also includes inflection information, such as the number, person and case XXX, which makes it much better suited to agglutinative languages than Penn Treebank POS tags. One shortcoming of the KR code is that it does not differenciate between common and proper nouns. Since in Hungarian only proper nouns are capitalized, we can usually decide whether a noun is proper or not based on the initial letter. However, this rule cannot be used if the noun is at the beginning of a sentence, as words at the beginning of sentences are always capitalized. Hence, all sentences that begin with nouns have been removed from the corpus.

@@

% Corpus sizes, performance, tagging conventions
% Hun -> not utf-8, loss of precision?
%measuring Wikipedia's inconsistency using n-gram tag variation (\cite{Nothman:09})
%ez jó mérőszám lehet a gold standard korpuszok összehasonlítására
%használhatjuk fordítva is: ha egy adott nucleus ugyanolyan n-gram környezetben nagyon sokszor van X-ként taggelve, és kevésszer Y-ként, akkor az Y-okat is átcsinálhatnánk X-szé

@@

To evaluate our corpora we used a maximum entropy NE-tagger \cite{Varga:07}, which was originally developed for labeling NEs in Hungarian texts, but it can be tuned for different languages, as well. Corpus-specific features (e.g.~NP chunks, Wikipedia links) were removed to get better comparability, so the feature set was as follows:

@@

However, Wikipedia-derived corpora can also be used for improving NER performance in other ways. First, like e.g.~\cite{Toral:06} we collected huge gazetteer lists from the corpus for each NE category, which improved the overall F-measure given to the NE-tagger training and testing on CoNLL dataset. A second trial was labeling the CoNLL datasets by the model trained on Wikipedia corpus, and giving these labels as extra features to the next CoNLL train. Both methods result in improved overall F-measure on CoNLL test set.

@@

az eredeti DBpedia osztályokat is megtarthatnánk, hiszen nem mindig célravezető a CoNLL osztályok használata, mivel azok elég tág kategóriák, amikbe olyan dolgok is tartoznak, amik nagyon eltérőek is lehetnek

@@

\bibitem[\protect\citename{Balasuriya \bgroup et al.\egroup}2009]{Balasuriya:09}
Dominic Balasuriya, Nicky Ringland, Joel Nothman, Tara Murphy, James R. Curran
\newblock 2009.
\newblock Named Entity Recognition in Wikipedia.
\newblock In: {\em Proceedings of the 2009 Workshop on the People's Web Meets NLP, ACL-IJCNLP}, pages 10--18.

\bibitem[\protect\citename{Csendes \bgroup et al.\egroup}2004]{Csendes:04} 
Dóra Csendes, János Csirik, Tibor Gyimóthy.
\newblock 2004.
\newblock The Szeged Corpus: A POS tagged and Syntactically Annotated Hungarian Natural Language Corpus. 
\newblock In: {\em Proceedings of TSD 2004}, vol. 3206, pages 41--49.

@@

\bibitem[\protect\citename{Kiss and Strunk}2002]{Kiss:06}
Tibor Kiss, Jan Strunk.
\newblock 2006.
\newblock Unsupervised Multilingual Sentence Boundary Detection. 
\newblock In: {\em Computational Linguistics}, 32 (4): pages 485--525.

\bibitem[\protect\citename{Kornai \bgroup et al.\egroup}2004]{Kornai:04}
András Kornai, Péter Rebrus, Péter Vajda, Péter Halácsy, András Rung, Viktor Trón.
\newblock 2004.
\newblock Általános célú morfológiai elemző kimeneti formalizmusa (The output formalism of a general-purpose morphological analyzer).
\newblock In: {\em Proceedings of the 2nd Hungarian Computational Linguistics Conference}.

\bibitem[\protect\citename{Loper and Bird}2002]{Loper:02}
Edward Loper, Steven Bird.
\newblock 2002.
\newblock NLTK: the Natural Language Toolkit. 
\newblock In: {\em Proceedings of the ACL-02 Workshop on Effective tools and methodologies for teaching natural language processing and computational linguistics}, Volume 1, pages 63--70.

\bibitem[\protect\citename{Nothman \bgroup et al.\egroup}2009]{Nothman:09}
Joel Nothman and Tara Murphy and James R. Curran.
\newblock 2009.
\newblock Analysing Wikipedia and Gold-Standard Corpora for NER Training.
\newblock In: {\em Proceedings of the 12th Conference of the European Chapter of the ACL}, pages 612--620.

@@

\bibitem[\protect\citename{Toral and Mu\~noz}2006]{Toral:06}
A. Toral and R. Mu\~noz.
\newblock 2006.
\newblock A proposal to automatically build and maintain gazetteers for Named Entity Recognition by using Wikipedia.
\newblock In: {\em EACL 2006}.

\bibitem[\protect\citename{Trón \bgroup et al.\egroup}2005]{Tron:05}
Viktor Trón, György Gyepesi, Péter Halácsy, András Kornai, László Németh, Dániel Varga.
\newblock 2005.
\newblock Hunmorph: open source word analysis.
\newblock In: {\em Proceedings of the ACL 2005 Workshop on Software}.
